On the \note{penalty stabilization mechanism for upwind discontinuous Galerkin formulations of first order hyperbolic systems}

### 2017-07-30 docs/dg_penalty/revision/main.tex

\newcommand{\note}[1]{{\color{blue}#1}}
\newcommand{\remark}[1]{\textbf{\color{red}#1}}

@@

\date{}
%\author{Jesse Chan, T. Warburton}
%\title{A short note on the penalty flux parameter for first order discontinuous Galerkin formulations}

@@

When $\bm{A}_n$ is not continuous across faces, the penalty numerical flux can be generalized as follows \cite{ye2016discontinuous}
\[
(\bm{A}_n\bm{U})^* = \avg{\bm{A}_n\bm{U}} - \frac{\tau}{2} \bm{A}_n^T \jump{\bm{A}_n\bm{U}},
\]
where we define the normal jump and average
\[
\jump{\bm{A}_n\bm{U}}\coloneqq \sum_{i=1}^d\bm{n}_i \jump{ \bm{A}_i \bm{U}}, \qquad \avg{\bm{A}_n\bm{U}} \coloneqq \sum_{i=1}^d\bm{n}_i\avg{ \bm{A}_i \bm{U}}.
\]
If $\bm{A}_i$ is constant over each element $D^k$, we again have an energy estimate with a dissipative contribution from the penalty flux
\[
\sum_{D^k\in \Oh}\pd{}{t}\nor{\bm{U}}^2_{L^2\LRp{D^k}} = -\sum_{D^k \in \Oh} \frac{\tau}{2}\nor{\jump{\bm{A}_n\bm{U}}}^2_{L^2\LRp{\partial D^k}} \leq 0.
\]
The upwind flux can similarly be extended for discontinuous coefficients
\[
(\bm{A}_n\bm{U})^* = \avg{\bm{A}_n\bm{U}} - \frac{1}{2} \jump{\bm{V}\LRb{\Lambda}\bm{V}^{-1}\bm{U}},
\]
where the eigenvalue decompositions inside the jump is evaluated as 
\begin{align*}
&\jump{\bm{V}\LRb{\Lambda}\bm{V}^{-1}\bm{U}} = {\bm{V}^+\LRb{\Lambda}^+\LRp{\bm{V}^+}^{-1}\bm{U}^+} - {\bm{V}^-\LRb{\Lambda}^-\LRp{\bm{V}^-}^{-1}\bm{U}^-}\\
&\bm{A}_n^+ = \sum_{i=1}^d \bm{n}_i \bm{A}_i^+ = \bm{V}^+{\Lambda}^+\LRp{\bm{V}^+}^{-1}, \qquad \bm{A}_n^- = \sum_{i=1}^d \bm{n}_i \bm{A}_i^- = \bm{V}^-{\Lambda}^-\LRp{\bm{V}^-}^{-1}.
\end{align*} 
Finally, we note that the energy estimate changes when $\bm{A}_i$ varies over an element, though the penalty flux still adds a dissipative contribution to the right hand side \cite{kopriva2014energy}.  
}

>>>>

%\newcommand{\note}[1]{{\color{blue}#1}}
\newcommand{\note}[1]{#1}
\newcommand{\remark}[1]{\textbf{\color{red}#1}}

@@

\date{}
%\author{Jesse Chan, T. Warburton}
%\title{A short note on the penalty flux parameter for first order discontinuous Galerkin formulations}
\graphicspath{{./figs/}}

@@

When $\bm{A}_n$ is not continuous across faces, the penalty numerical flux can be generalized as follows \cite{ye2016discontinuous}
\[
(\bm{A}_n\bm{U})^* = \avg{\bm{A}_n\bm{U}} - \frac{\tau}{2} \bm{A}_n^T \jump{\bm{A}_n\bm{U}},
\]
where we define the normal jump and average
\[
\jump{\bm{A}_n\bm{U}}\coloneqq \sum_{i=1}^d\bm{n}_i \jump{ \bm{A}_i \bm{U}}, \qquad \avg{\bm{A}_n\bm{U}} \coloneqq \sum_{i=1}^d\bm{n}_i\avg{ \bm{A}_i \bm{U}}.
\]
If $\bm{A}_i$ is constant over each element $D^k$, we again have an energy estimate with a dissipative contribution from the penalty flux
\[
\sum_{D^k\in \Oh}\pd{}{t}\nor{\bm{U}}^2_{L^2\LRp{D^k}} = -\sum_{D^k \in \Oh} \frac{\tau}{2}\nor{\jump{\bm{A}_n\bm{U}}}^2_{L^2\LRp{\partial D^k}} \leq 0.
\]
%The upwind flux can similarly be extended for discontinuous coefficients
%\[
%(\bm{A}_n\bm{U})^* = \avg{\bm{A}_n\bm{U}} - \frac{1}{2} \jump{\bm{V}\LRb{\Lambda}\bm{V}^{-1}\bm{U}},
%\]
%where the eigenvalue decompositions inside the jump is evaluated as 
%\begin{align*}
%&\jump{\bm{V}\LRb{\Lambda}\bm{V}^{-1}\bm{U}} = {\bm{V}^+\LRb{\Lambda}^+\LRp{\bm{V}^+}^{-1}\bm{U}^+} - {\bm{V}^-\LRb{\Lambda}^-\LRp{\bm{V}^-}^{-1}\bm{U}^-}\\
%&\bm{A}_n^+ = \sum_{i=1}^d \bm{n}_i \bm{A}_i^+ = \bm{V}^+{\Lambda}^+\LRp{\bm{V}^+}^{-1}, \qquad \bm{A}_n^- = \sum_{i=1}^d \bm{n}_i \bm{A}_i^- = \bm{V}^-{\Lambda}^-\LRp{\bm{V}^-}^{-1}.
%\end{align*} 
Finally, we note that the energy estimate changes when $\bm{A}_i$ varies over an element, though the penalty flux still adds a dissipative contribution to the right hand side \cite{kopriva2014energy}.  
}
